Research

### 2024-01-23 index.qmd
fix link behaviour

The **Action, Cognition, and Metascience Lab** is an interdisciplinary research team investigating basic scientific questions about how the human brain controls and learns skilled actions. We study decision-making for action and practice factors supporting skill acquisition and maintenance in single- and multi-agent scenarios. We also conduct metascience research to gain important insights into research practices within kinesiology and sport science. We are located in the Ivor Wynne Centre, which is home to the [Department of Kinesiology](https://www.science.mcmaster.ca/kinesiology/) within the [Faculty of Science](https://www.science.mcmaster.ca/) at [McMaster University](https://www.mcmaster.ca/).

@@

<font color="#d08770">[January 22 2024].</font> **Paper accepted**. Roth, A.M., Lokesh, R., Tang, J., Buggeln, J.H., Smith, C., Calalo, J.A., Sullivan, S.R., Ngo, T., St. Germain, L., Carter, M.J., & Cashaback, J.G.A. Punishment leads to greater sensorimotor learning but less movement variability compared to reward. *Neuroscience*. <https://doi.org/10.1016/j.neuroscience.2024.01.004>

@@

<font color="#d08770">[September 6 2023].</font> **Paper accepted**. Roth, A.M., Calalo, J.A., Lokesh, R., Sullivan, S.R., Grill, S., Jeka, J.J., van der Kooij, K., Carter, M.J, & Cashaback, J.G.A. Reinforcement-based processes actively regulate motor exploration along redundant solution manifolds. *Proceedings of the Royal Society B*. <https://doi.org/10.1098/rspb.2023.1475>

>>>>

The **Action, Cognition, and Metascience Lab** is an interdisciplinary research team investigating basic scientific questions about how the human brain controls and learns skilled actions. We study decision-making for action and practice factors supporting skill acquisition and maintenance in single- and multi-agent scenarios. We also conduct metascience research to gain important insights into research practices within kinesiology and sport science. We are located in the Ivor Wynne Centre, which is home to the [Department of Kinesiology](https://www.science.mcmaster.ca/kinesiology/){target="_blank"} within the [Faculty of Science](https://www.science.mcmaster.ca/){target="_blank"} at [McMaster University](https://www.mcmaster.ca/){target="_blank"}.

@@

<font color="#d08770">[January 22 2024].</font> **Paper accepted**. Roth, A.M., Lokesh, R., Tang, J., Buggeln, J.H., Smith, C., Calalo, J.A., Sullivan, S.R., Ngo, T., St. Germain, L., Carter, M.J., & Cashaback, J.G.A. Punishment leads to greater sensorimotor learning but less movement variability compared to reward. *Neuroscience*. [https://doi.org/10.1016/j.neuroscience.2024.01.004](https://doi.org/10.1016/j.neuroscience.2024.01.004){target="_blank"}

@@

<font color="#d08770">[September 6 2023].</font> **Paper accepted**. Roth, A.M., Calalo, J.A., Lokesh, R., Sullivan, S.R., Grill, S., Jeka, J.J., van der Kooij, K., Carter, M.J, & Cashaback, J.G.A. Reinforcement-based processes actively regulate motor exploration along redundant solution manifolds. *Proceedings of the Royal Society B*. [https://doi.org/10.1098/rspb.2023.1475](https://doi.org/10.1098/rspb.2023.1475){target="_blank"}

### 2024-01-23 news.qmd
update news with new paper
fix link behaviour

@@

<font color="#d08770">[September 6 2023].</font> **Paper accepted**.   Roth, A.M., Calalo, J.A., Lokesh, R., Sullivan, S.R., Grill, S., Jeka, J.J., van der Kooij, K., Carter, M.J, & Cashaback, J.G.A. Reinforcement-based processes actively regulate motor exploration along redundant solution manifolds. *Proceedings of the Royal Society B*.

@@

<font color="#d08770">[June 16 2023].</font> **New preprint**. McKay, B., Corson, A.E., Seedu, J., De Faveri, C.S., Hasan, H., Arnold, K., Adams, F.C., & Carter, M.J. Reporting bias, not external focus: A robust Bayesian meta-analysis of the attentional focus literature. *SportR*$\chi$*iv*. doi: <https://doi.org/10.51224/SRXIV.304>

<font color="#d08770">[May 26 2023].</font> **Paper accepted**. Lokesh, R., Sullivan, S.R., St. Germain, L., Roth, A.M., Calalo, J.A., Buggeln, J., Ngo, T., Marchhart, V.R.F., Carter, M.J, & Cashaback, J.G.A. Visual accuracy dominates over haptic speed for state estimation of a partner during collaborative sensorimotor interactions. *Journal of Neurophysiology*.

<font color="#d08770">[May 19 2023].</font> **New preprint**. St. Germain, L., McKay, B., Tandon, C., Seedu, J., Barbera, L., Carrillo, C., Brown, D.M.Y., & Carter, M.J. Autonomy-supportive instructional language does not enhance skill acquisition compared to controlling instructional language. *SportR*$\chi$*iv*. doi: <https://doi.org/10.51224/SRXIV.298>

<font color="#d08770">[April 13 2023].</font> **Paper accepted**. McKay, B., Bacelar, M.F.B., Parma, J.O., Miller, M.W., & Carter, M.J. The combination of reporting bias and underpowered study designs has substantially exaggerated the motor learning benefits of self-controlled practice and enhanced expectancies: A meta-analysis. *International Review of Sport and Exercise Psychology*.

>>>>

<font color="#d08770">[January 22 2024].</font> **Paper accepted**. Roth, A.M., Lokesh, R., Tang, J., Buggeln, J.H., Smith, C., Calalo, J.A., Sullivan, S.R., Ngo, T., St. Germain, L., Carter, M.J., & Cashaback, J.G.A. Punishment leads to greater sensorimotor learning but less movement variability compared to reward. *Neuroscience*. [https://doi.org/10.1016/j.neuroscience.2024.01.004](https://doi.org/10.1016/j.neuroscience.2024.01.004){target="_blank"}

@@

<font color="#d08770">[September 6 2023].</font> **Paper accepted**. Roth, A.M., Calalo, J.A., Lokesh, R., Sullivan, S.R., Grill, S., Jeka, J.J., van der Kooij, K., Carter, M.J, & Cashaback, J.G.A. Reinforcement-based processes actively regulate motor exploration along redundant solution manifolds. *Proceedings of the Royal Society B*. [https://doi.org/10.1098/rspb.2023.1475](https://doi.org/10.1098/rspb.2023.1475){target="_blank"}

@@

<font color="#d08770">[June 16 2023].</font> **New preprint**. McKay, B., Corson, A.E., Seedu, J., De Faveri, C.S., Hasan, H., Arnold, K., Adams, F.C., & Carter, M.J. Reporting bias, not external focus: A robust Bayesian meta-analysis of the attentional focus literature. *SportR*$\chi$*iv*. [https://doi.org/10.51224/SRXIV.304](https://doi.org/10.51224/SRXIV.304){target="_blank"}

<font color="#d08770">[May 26 2023].</font> **Paper accepted**. Lokesh, R., Sullivan, S.R., St. Germain, L., Roth, A.M., Calalo, J.A., Buggeln, J., Ngo, T., Marchhart, V.R.F., Carter, M.J, & Cashaback, J.G.A. Visual accuracy dominates over haptic speed for state estimation of a partner during collaborative sensorimotor interactions. *Journal of Neurophysiology*. [https://doi.org/10.1152/jn.00053.2023](https://doi.org/10.1152/jn.00053.2023){target="_blank"}

<font color="#d08770">[May 19 2023].</font> **New preprint**. St. Germain, L., McKay, B., Tandon, C., Seedu, J., Barbera, L., Carrillo, C., Brown, D.M.Y., & Carter, M.J. Autonomy-supportive instructional language does not enhance skill acquisition compared to controlling instructional language. *SportR*$\chi$*iv*. [https://doi.org/10.51224/SRXIV.298](https://doi.org/10.51224/SRXIV.298){target="_blank"}

<font color="#d08770">[April 13 2023].</font> **Paper accepted**. McKay, B., Bacelar, M.F.B., Parma, J.O., Miller, M.W., & Carter, M.J. The combination of reporting bias and underpowered study designs has substantially exaggerated the motor learning benefits of self-controlled practice and enhanced expectancies: A meta-analysis. *International Review of Sport and Exercise Psychology*. [https://doi.org/10.1080/1750984X.2023.2207255](https://doi.org/10.1080/1750984X.2023.2207255){target="_blank"}

### 2024-01-23 research.qmd
fix link behaviour

Our research is supported by the [Natural Sciences and Engineering Research Council of Canada](https://www.nserc-crsng.gc.ca/), the [Canadian Foundation for Innovation](https://www.innovation.ca/), and the [Ontario Research Fund](https://www.ontario.ca/page/ontario-research-fund-research-infrastructure).

>>>>

Our research is supported by the [Natural Sciences and Engineering Research Council of Canada](https://www.nserc-crsng.gc.ca/){target="_blank"}, the [Canadian Foundation for Innovation](https://www.innovation.ca/){target="_blank"}, and the [Ontario Research Fund](https://www.ontario.ca/page/ontario-research-fund-research-infrastructure){target="_blank"}.
